air4children: Artificial Intelligence and Robotics for Children

### 2021-03-06 slides/sources/air4children.tex
re-organise layout of the slides
#5 adds notes for images to be added
incorporates montesory and team figures
polish structure a bit the strucutre
adds robots and use same name for AIR4Children in the slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching materials}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Subsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Lastname N. YEAR in journal of...}
\begin{frame}{Teaching materials}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v01.png}
        %\caption{}
      \end{figure}
\end{frame}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{AIR4Children}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{AIR for Children}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Savage N. 2021 in Nature}
\begin{frame}{Title}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Savage N. 2021 in Nature}
\begin{frame}{Title}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v01.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Teaching Materials}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Lastname N. YEAR in journal of...}
\begin{frame}{Montessori}

    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Lastname N. YEAR in journal of...}
\begin{frame}{Teaching materials based on Montessori}
* add image that represents montesory skills
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v01.png}
        %\caption{}
      \end{figure}
\end{frame}
}
